Rapid response of mesophyll conductance to light availability allows shade leaves to take advantage of sunflecks

### 2015-09-23 manuscript/manuscript_wtc3.Rmd
attempted tp add pixie dust to table
started energy balance script

```{r global data/sourcing , include=FALSE}
source("functions and packages/functions.R")
source("functions and packages/packages.R")
source("master_scripts/plot_objects.R")
library(pander)

>>>>

```{r global data/sourcing , include=FALSE}
source("functions and packages/functions.R")
source("functions and packages/packages.R")
source("master_scripts/plot_objects.R")
library(pixiedust)

##read table ready dataframes
# resourcetab <- read.csv("master_scripts/resource_table.csv")
# getab <- read.csv("master_scripts/ge_table.csv")
